%-------------------------
% Resume - Elyes Darouich
% Simple One-Page Style
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{xcolor}

% Page margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Color definitions
\definecolor{darkgray}{RGB}{64, 64, 64}
\definecolor{lightgray}{RGB}{128, 128, 128}
\definecolor{sectioncolor}{RGB}{0, 102, 204}

% Section formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large\color{sectioncolor}\bfseries
}{}{0em}{}[\color{sectioncolor}\titlerule \vspace{-8pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=-2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Elyes Darouich} \\ \vspace{3pt}
    \small \textbf{Software Engineer --- Full-Stack Developer --- Problem Solver}
    \\ \vspace{5pt}
    \small 
    \faMapMarker\ Bizerte, Tunisia \quad
    \faPhone\ +216 94 906 400 \quad
    \faEnvelope\ \href{mailto:skyrexcgaming@gmail.com}{skyrexcgaming@gmail.com}
    \\ \vspace{2pt}
    \small
    \faLinkedin\ \href{https://linkedin.com/in/elyesdarouich}{linkedin.com/in/elyesdarouich} \quad
    \faGithub\ \href{https://github.com/ElyesD1}{github.com/ElyesD1} \quad
    \faGlobe\ \href{https://elyesdarouichportfolio.vercel.app}{Portfolio}
\end{center}

%----------PROFESSIONAL SUMMARY----------
\section{Professional Summary}
\small{Mobile Software Engineer with expertise in iOS (SwiftUI, UIKit), Android (Kotlin), and cross-platform development (Flutter). Proficient in full-stack web development with React, NestJS, Next.js, and Spring Boot. Experienced in AI/ML integration, DevOps practices, and agile methodologies.}

%----------TECHNICAL EXPERTISE----------
\section{Technical Expertise}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Mobile Development}{: Swift (SwiftUI, UIKit, Core Data, MapKit), Kotlin (Jetpack, Android SDK), Flutter, Dart} \\
     \textbf{Frontend \& Web}{: TypeScript, React, Next.js, JavaScript, HTML/CSS, Tailwind CSS} \\
     \textbf{Backend \& APIs}{: NestJS, Node.js, Express, REST APIs, WebSockets, GraphQL} \\
     \textbf{Databases}{: MongoDB, Firebase, MySQL, PostgreSQL} \\
     \textbf{Cloud \& DevOps}{: Docker, GitHub Actions, Vercel, Nginx, Linux} \\
     \textbf{AI Integration}{: Google Gemini API, OpenAI, TensorFlow Lite} \\
     \textbf{Tools}{: Git/GitHub, Figma, Postman, Jira, VS Code, Xcode, Android Studio}
    }}
\end{itemize}

%----------EXPERIENCE----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Mobile \& Backend Engineering Intern}{Summer 2025}
      {Talan Tunisia}{Tunis, Tunisia}
      \resumeItemListStart
        \resumeItem{Built ProjectFlow, a cross-platform project management platform using Flutter and NestJS deployed in production.}
        \resumeItem{Implemented real-time collaboration with WebSockets \& Socket.IO for live updates, chat, and Kanban boards.}
        \resumeItem{Integrated Google OAuth + JWT authentication with role-based access control and AI assistant using Gemini 2.0.}
        \resumeItem{Set up Dockerized deployments with GitHub Actions CI/CD achieving <150ms API response time for 100+ users.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Flutter Developer Intern}{Summer 2023}
      {Vatech WABAG}{Tunis, Tunisia}
      \resumeItemListStart
        \resumeItem{Developed cross-platform employee leave management app with secure authentication and role-based access.}
        \resumeItem{Integrated Firebase real-time push notifications and optimized performance for Android and iOS.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%----------EDUCATION----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Computer Engineering - Mobile Development}{2021 -- Present}
      {ESPRIT (École Supérieure Privée d'Ingénierie et de Technologies)}{Ariana, Tunisia}
      \resumeItemListStart
        \resumeItem{5th year student, specialized in mobile development and cross-platform solutions (iOS, Android, Flutter).}
        \resumeItem{Advanced coursework in software architecture, AI integration, DevOps, and agile methodologies.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Baccalauréat in Computer Science}{2020 -- 2021}
      {Lycée Jeune Fille}{Bizerte, Tunisia}
      \resumeItemListStart
        \resumeItem{Graduated with specialization in Computer Science and Mathematics.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------KEY PROJECTS----------
\section{Key Projects}
  \resumeSubHeadingListStart
  
    \resumeProjectHeading
      {\textbf{SquadLink} | \emph{Next.js, NestJS, MongoDB, Socket.io, Riot API, Discord Bot}}{2025--2026}
      \resumeItemListStart
        \resumeItem{Full-stack esports platform with real-time matchmaking, live tracking, and player analytics.}
        \resumeItem{Built WebSocket notifications and automated Discord bot with voice integration and smart MongoDB caching.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\textbf{ProjectFlow} | \emph{Flutter, NestJS, MongoDB, Gemini AI, WebSockets}}{2024--2025}
      \resumeItemListStart
        \resumeItem{AI-powered project management platform with real-time Kanban, drag-and-drop, analytics dashboard, and team communication.}
      \resumeItemListEnd
      
    \resumeProjectHeading
      {\textbf{Dialex} | \emph{SwiftUI, Kotlin, NestJS, MongoDB}}{2024--2025}
      \resumeItemListStart
        \resumeItem{Cross-platform language learning app with interactive exercises, voice recognition, and gamification features.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%----------EDUCATION----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Computer Engineering --- Mobile Development Specialization}{2021 -- Present}
      {ESPRIT, Tunisia}{5th Year Engineering Student}
  \resumeSubHeadingListEnd

%----------LANGUAGES & ADDITIONAL----------
\section{Languages \& Additional}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Arabic (Native), French (B2), English (C1)} \\
     \textbf{Certifications}{: AWS Academy Graduate --- Cloud Foundations, Hashgraph Developer Certificate}
    }}
\end{itemize}

\end{document}
